A Quantitative Genetic Linked Selection Model of the Negative Selection Process in Humans

### 2023-07-10 manuscript/manuscript.tex
abstract draft

    Previous work has shown that negative selection against the steady influx
    of deleterious mutations is the predominant process shaping genome-wide
    patterns of genetic diversity in humans. This process leaves a ``linked
    selection signal"

    The classic population genetic
    model of this process, background selection, considers

    % TODO: emphasize connection to nearly neutral theory

    % uniting quant gen/fitness variation, linked selection, and substitution
    % The interesting thing about connecting all these models is that we might
    % have hope of calibrating these models to the true process.
\end{abstract}

>>>>

    Across the human genome, there are large-scale fluctuations in genetic
    diversity caused by the indirect effects of selection. This can be thought
    of as a ``linked selection signal" that is shaped by selection acting on
    the placement of functional regions and recombination rates along the
    genome. Previous work has shown that negative selection against the steady
    influx of new deleterious mutations into conserved regions is the
    predominant mode of selection generating this signal in humans. However,
    the theoretic model that underpins these results, classic Background
    Selection theory, is only applicable when new mutations are so deleterious
    that they cannot drift up in frequency and ultimately fix in the
    population. Here, we develop an alternate theoretic basis for genome-wide
    linked selection based on a quantitative genetics view, which considers the
    distribution of additive fitness variance along the genome. Using a recent
    model that jointly predicts the equilibrium fitness variance and
    substitution rate due to deleterious mutations, we fit this model to
    samples from three human populations to estimate the distribution of
    selection coefficients and mutation rate. While our model can accommodate
    weaker selection, we find consistent evidence across all populations of
    very strong selection against deleterious mutations. We also find that our
    model's predicted substitution rates are qualitatively consistent with
    observed divergences in features under weak selective constraint like
    introns and UTRs, but we observe vastly more substitutions in regions under
    strong selective constrain, consistent with positive selection. While our
    model explains up to 67\% of the out-sample variance in diversity at the
    megabase scale, we find evidence of residual strong selection against
    loss-of-function variants, indicating the dominant role negative selection
    plays in the human genome. Altogether, our genome-wide model of the linked
    selection is a step towards uniting evolutionary quantitative genetics with
    the molecular evolutionary processes.

\end{abstract}
